Pillar 1 - Sequential Pattern Mining

### 2019-01-17 Pillar 1 - Sequential Pattern Mining.Rmd
rule induction for courses

maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
```{r}
frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
summary(frequent_trajectories)
as(frequent_trajectories, "data.frame")

@@

>>>>

maxsize:  an integer value specifying the maximum number of items of an element of a sequence (default 10, range > 0).
maxlen:   an integer value specifying the maximum number of elements of a sequence (default 10, range > 0).
mingap:   an integer value specifying the minimum time difference between consecutive elements of a sequence (default none, range >= 1).
maxgap:   an integer value specifying the maximum time difference between consecutive elements of a sequence (default none, range >= 0).
maxwin:   an integer value specifying the maximum time difference between any two elements of a sequence (default none, range >= 0).
```{r}
summary(my_transactions)

frequent_trajectories <- cspade(my_transactions, parameter = list(support = 0.01), control   = list(verbose = TRUE))
#Looking into this: 
summary(frequent_trajectories)
as(frequent_trajectories, "data.frame")

@@

```{r}
rules <- ruleInduction(frequent_trajectories, confidence = 0.2, #we need to play with the parameters.
                    control    = list(verbose = TRUE))
as(rules, "data.frame") %>%
  arrange(desc(lift))
```
